Bayes network classifiers for fMRI

### 2012-10-16 article/article.tex
Article update (on feature selection)

%% indicate IEEE Member or Student Member in form indicated below
\author{Mattijs Meiboom, Robin Mills, Tijn Schouten, Spyros Ioakeimidis}
\authorfooter{
\item
  Mattijs Meiboom is with University of Groningen, E-mail: m.meiboom@student.rug.nl.
\item
  Robin Mills is with University of Groningen, E-mail: .
\item
  Tijn Schouten is University of Groningen, E-mail: t.m.schouten.2@student.rug.nl.
\item
  Spyros Ioakeimidis  is with University of Groningen, E-mail: spyrosikmd@gmail.com.
}

@@

- same for each algorithm:
    - supervised learning
        - feature selection
        - classification / discrimination / scoring function
    - naive bayes
    - multivariate
    - pca

@@

In total, we have data available for approximately 4000 voxels per scan, 54 scans per trial, 40 trials per subject, 6 subjects.

@@

>>>>

%% indicate IEEE Member or Student Member in form indicated below
\author{Mattijs Meiboom, Robin Mills, Tijn Schouten, Spyros Ioakeimidis}
\authorfooter{
\item
  Mattijs Meiboom is with University of Groningen, E-mail: m.meiboom@student.rug.nl.
\item
  Robin Mills is with University of Groningen, E-mail: .
\item
  Tijn Schouten is with University of Groningen, E-mail: t.m.schouten.2@student.rug.nl.
\item
  Spyros Ioakeimidis  is with University of Groningen, E-mail: spyrosikmd@gmail.com.
}

@@

@@

In total, we have data available for approximately 4000 voxels per scan, 54 scans per trial, 40 trials per subject, 6 subjects. Voxels have been grouped into 25 regions of interest (see \textit{Feature selection}) that may be of use for analysis.

@@

\subsection{Feature selection}
%Inspired by: http://www.brainvoyager.com/bvqx/doc/UsersGuide/WebHelp/Content/MVPATools/MVPA_Basic_Concepts.htm
Typical input for the machine learning algorithms discussed in this paper consists of a number of feature vectors, one for each fMRI scan. Such a feature vector $\vec{x}$ contains measures for the $N$ features we use to represent that scan and is derived from our input data. In the most basic case, we could use the entire set of voxels belonging to a scan, resulting in a feature vector containing potentially (hundreds of) thousands of features.
In the case that we have a very large dimension of features combined with only a limited amount of scans, our classifier may have difficulty learning the right classification function. This problem is formally known as the \textit{Hughes effect}\cite{Hughes1054102} which states that the predictive power of a machine learning algorithm decreases as the dimensionality increases with a fixed number of training examples.

So how do we cope with this problem? On common solution is to reduce $|\vec{x}|$ by only using voxels belonging to a specific region of interest (ROI). However, this requires us to known which regions are actually of interest \textit{a priori}.
- ROIs, means, stddev, skew, kurtosis?

- same for each algorithm:
    - supervised learning
        - feature selection
            - ROI vs Whole Brain
        - classification / discrimination / scoring function
    - naive bayes
    - multivariate
    - multi-voxel pattern analysis
    - pca
